Functions Created

### 2017-08-17 Hours.Rmd
used stepAIc with backwards/forward sepwise selection, added interaction terms, recoded category variable
plotted residuals, updated hours
cross validation, updated hours
updating hours

>>>>

8/11/2017 | 5.5 | 10:30-4:00PM | Researched more model fitting functions, recoded category variable
8/11/2017 | 2 | 8:00-10:00PM | Plotted residuals + predicted on test data set
8/15/2017 | 9.5 | 11:00-8:30PM | Cross validation + model fitting 
8/16/2017 | 5 | 10:30-3:30PM | Wrote function for cross validation 
8/16/2017 | 2.5 | 7:00-9:30PM | Fit model to full data set, wrote function to take data, fit model, and get predicted survival probabilities
